PMV: Comparing the prediction accuracy of ISO 7730:2005 and ASHRAE 55:2023

### 2023-09-05 Manuscript/src/sections/results.tex
accepted some of the comments from Stefano

\subsection{Sources of Error}\label{subsec:sources-of-error}
In this Section, we identify some of the main reasons that could explain the difference in the results from the two \ac{pmv} models when compared against the \ac{tsv} available in the \ac{db2}.
Moreover, we tried to explain why we observed that the \ac{pmv-ce} model has a lower accuracy than the \ac{pmv} in predicting thermal sensation.
The issues are not reported in order of importance and more research is needed to determine how to improve the overall accuracy of the \ac{pmv} model.

\paragraph{Lack of Data}
T.

>>>>

\subsection{Sources of Error}\label{subsec:sources-of-error}
In this Section, we identify some of the main reasons that could explain the difference in the results from the two \ac{pmv} models when compared against the \ac{tsv} available in the \ac{db2}.
Moreover, we tried to explain why we observed that the \ac{pmv-ce} model has a lower accuracy than the \ac{pmv} in predicting thermal sensation.
The issues are reported in order of importance of what we believe may affect the accuracy of the model.
More research is needed to determine how to improve the overall accuracy of the \ac{pmv} model.
